### 2014-11-24 papers/paper7.tex

>>>>

  \section*{Introduction}
  The hardest part of making a game has always been the engineering. In past times, game engineering was mainly about low-level optimization - writing code that would run quickly on the target computer, leveraging clever tricks whenever possible. But in the past ten years, games have ballooned in complexity.

  \section*{Project size and complexity}

    \subsubsection*{Tools}

    \subsubsection*{Workflow}

    \subsubsection*{Multiplatform Development}

    \subsubsection*{Third-Party Components}

    \subsubsection*{Full-Figure Options}

  \section*{Highly Domain-Specific Requirements}

    \subsubsection*{Engine Code}

    \subsubsection*{Crosscutting Concerns}

    \subsubsection*{Depth of Simulation}

    \subsubsection*{Profiling}

    \subsubsection*{Risk}
